Real-space computation of $E$/$B$-mode maps I: Formalism and Compact Kernels

### 2018-05-29 articles/formalism/sections/introduction.tex
Fixed reionizations -> recombination

\section{Introduction}
During reionization, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.  The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature \citep{1997NewA....2..323H}.  The standard analysis technique converts the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, which are easier to compare to theory.  The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations.  Thus any $B$-modes that appear must be from:
% Need citations for all...
(1) primordial tensor perturbations (gravitational waves), which reveal the energy scale of inflation
\citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
(2) lensing of $E$-modes, which helps to reveal the distribution of matter in the universe;
(3) foregrounds (especially Galactic synchrotron and dust emission)
\citep{2016A&A...586A.133P};
(4) unknown systematic problems in the data;
(5) unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
\citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.

>>>>

\section{Introduction}
During recombination, the Cosmic Mircowave Background undergoes Thomson scattering that leaves it with $\sim 5$ percent linear polarization.  The polarization signal contains information about the plasma velocity and provides cosmological constraints independent from the signal in temperature \citep{1997NewA....2..323H}.  The standard analysis technique converts the Stokes parameters of polarization into scalar ($E$) and pseudo-scalar ($B$) modes, which are easier to compare to theory.  The pseudo-scalar $B$ mode is particularly important because it cannot be generated by primordial scalar pertubations.  Thus any $B$-modes that appear must be from:
% Need citations for all...
(1) primordial tensor perturbations (gravitational waves), which reveal the energy scale of inflation
\citep{1997PhRvD..56..596H,1997PhRvL..78.2054S};
(2) lensing of $E$-modes, which helps to reveal the distribution of matter in the universe;
(3) foregrounds (especially Galactic synchrotron and dust emission)
\citep{2016A&A...586A.133P};
(4) unknown systematic problems in the data;
(5) unknown, exotic phenemena like cosmic birefringence or primordial magnetic fields
\citep{1996ApJ...469....1K,1999PhRvL..83.1506L,2004ApJ...616....1C,2014MNRAS.438.2508P}.
